More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-03-23 2016-Weak-FH-Bisim/WeakBisim.tex
c est pas K c est J dans la footnote
small changes to OTs
2 new fashion OTs in page 6 & 7

  \includegraphics[width=7cm]{XFIG/Transport}
  \hspace{0.5cm}
 \includegraphics[width=4.5cm]{XFIG/TransportSpec}
  \caption{Schema and specification of the protocol }  \label{schema:ABP-pnets}
%\end{minipage}
  \vspace{1cm}
%\begin{minipage}{6cm}
  \centerline{\includegraphics[width=11cm]{XFIG/ABP3-Schema}}
  \caption{Composed pNet with the ABP protocol}  \label{schema:ABP-composed}
%\end{minipage}

@@

\TODO{rewrite example with new OTs}
\begin{example}\emph{An open-transition.}
  \label{OT:ABP}
  The \texttt{ABP} pNet of Fig. \ref{schema:ABP-composed} has 2 controllers and 2 holes. One of its possible open-transition is:

 \smallskip
 $  OT_2  = \openrule{
                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
                            \xrightarrow{in(?m,?b)}_{M1}
                      }
  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
    { \OTarrow{\ostate{1,0,0,0}\underline{send(m,b)}} \ostate{2,1,0,0}}
  $
\end{example}

@@

	The second rule deals with pNet nodes: for each possible
	synchronisation vector applicable to the rule subject, the premisses
	include one {\em open transition} for each sub-pNet involved , one possible
	{\em action} for each Hole involved, and the predicate relating these
	with the resulting action of the vector. The sub-pNets involved are split between two 
	sets, $I_2$ for subnets that are pLTSs, and $I_1$ for the others, $J$ is the set of 
	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{\alpha_m^{m 
	\in M}}{\alpha'}{e_b}$ is a synchronisation vector  of \pNet  then $K=M\cap 
	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus K \setminus 
	I_2$}.

>>>>

  \includegraphics[width=7cm]{XFIG/Transport}
  \hspace{0.5cm}
 \includegraphics[width=4.5cm]{XFIG/TransportSpec}
  \caption{\TODO{Replace by various versions of the media} }  \label{schema:ABP-pnets}
%\end{minipage}
  \vspace{1cm}
%\begin{minipage}{6cm}
  \centerline{\includegraphics[width=11cm]{XFIG/ABP4-Schema}}
  \caption{Composed pNet with the ABP protocol}  \label{schema:ABP-composed}
%\end{minipage}

@@

\TODO{rewrite example with new OTs}
\begin{example}\emph{An open-transition.}
  \label{OT:ABP}
  The \texttt{Protocol} pNet of Fig. \ref{schema:ABP-composed} has 4 controllers and no holes. One of its possible open-transition (the sender sending $m,b$ to the medium) is:

 \smallskip
 $  OT_2  = \openrule{
%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
   %                           \xrightarrow{in(?m,?b)}_{M1}
      \emptyset; Pred=[m=s_1\_m, b=s_1\_sb];  Post=\{m_1\_m:=m, m_1\_b:=b\}
                      }
  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
    {Prot_1 \OTarrow{\tau} Prot_2}
  $

At the upper level, the $ABP$ pNet has 2 holes and and $Protocol$ has a subnet. One of its possible transition (synchronizing the hole $P$ with the $Protocol$) is:
 \smallskip
 $  OT_1  = \openrule{
%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
%                            \xrightarrow{in(?m,?b)}_{M1}
      \{\xrightarrow{send(m)}_P\}; Pred=True; Post=\{s1\_m:=m\}
                      }
  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
    {ABP_1 \OTarrow{\underline{send(m)}} ABP_2}
  $
\end{example}

@@

	The second rule deals with pNet nodes: for each possible
	synchronisation vector applicable to the rule subject, the premisses
	include one {\em open transition} for each sub-pNet involved , one possible
	{\em action} for each Hole involved, and the predicate relating these
	with the resulting action of the vector. The sub-pNets involved are split between two 
	sets, $I_2$ for subnets that are pLTSs, and $I_1$ for the others, $J$ is the set of 
	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{\alpha_m^{m 
	\in M}}{\alpha'}{e_b}$ is a synchronisation vector  of \pNet\  then $J=M\cap 
	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus J \setminus 
	I_2$}.
